%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This is a modified ONE COLUMN version of
% the following template:
%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \documentclass[11pt]{deedy-resume-openfont}

    \begin{document}
    
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Profile 
%     - DevOps / Platform Engineer
%     - DevOps Engineer – Azure Infrastructure
%     - Cloud DevOps Engineer
%     - Devops /Ansible Automation Engineer
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \sectionsep
\namesection{Alexander Acevedo}{DevOps Engineer}{Montreal, QC | (438) 993-6121  alex.devops.email@gmail.com  \href{https://www.linkedin.com/in/aa-devops}{linkedin.com/in/aa-devops}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%	    Summary (optional)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{0.8cm}
\section{About me}
\vspace{2pt}
% \noindent\makebox[\linewidth]{\rule{\paperwidth}{0.5pt}}
\begin{tightemize}
	\item 8+ years in software development, with a strong DevOps/SRE focus over the last 6 years.
	\item Proven experience designing and implementing CI/CD solutions using Azure DevOps and GitHub Actions.
	\item Hands-on experience with Infrastructure as Code (IaC) using Terraform and HashiCorp Cloud Platform to orchestrate deployments of complex cloud environments.
	\item Strong understanding of Cloud Landing Zone design principles, including architecture, management group hierarchy, networking, access control, security, and monitoring.
	\item Expert in branching strategies, semantic versioning (SemVer), and artifact management to maintain consistent, reliable, and traceable software releases.
\end{tightemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Experience
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{0.8cm}
\section{Work Experience}
\sectionsepsmall
\runsubsection{Desjardins}\descript{| Cloud Platform / DevOps Engineer}\hfill \location{Montreal, QC | 2022 – Present}
\begin{tightemize}
	\item Builds enterprise-scale Azure infrastructure as code, managing 3 connectivity hubs, 20+ business landing zones, and 50+ application landing zones across multi-tenant, multi-region, and multi-environment setups, ensuring scalable and reliable cloud operations.
	\item Standardize delivery infrastructure by developing and maintaining a modular Terraform ecosystem, including over 20 reusable lower-level modules and 3 higher-level meta-modules, to ensure consistent and compliant configurations.
	\item Accelerates delivery cycles by designing, developing, and maintaining GitHub Workflows for cloud deployment processes.
	\item Reduces internal Jira Service Desk change requests by re-engineering the delivery strategy of frequently changing cloud resources.
	\item Mentor 10 team members on a new Terraform/GitHub deployment framework, enabling autonomous management of cloud platform operations.
\end{tightemize}
\sectionsep
\projets{Projet(s):}{Cloud Transformation Program, Connectivity Landing Zone (Hub-Spoke), Business Landing Zone}
\sectionsep
\runsubsection{LGI Healthcare Solutions}\descript{| DevOps Integrator}\hfill \location{Montreal, QC | 2021 – 2022}
\begin{tightemize}
	\item Accelerated deployment cycles for 3 SaaS products by implementing a delivery-as-code approach in Azure DevOps, automating build, promotion, and release pipelines.
	\item Defined and implemented standardized versioning and branching strategies, improving release traceability and alignment with project requirements.
\end{tightemize}
\sectionsep
\projets{Projet(s):}{Intellium, Strom, EspressoGo}
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% This content will start on the next page
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\runsubsection{LGI Healthcare Solutions}\descript{| FullStack Developer}\hfill \location{Montreal, QC | 2018 – 2021}
\begin{tightemize}
	\item Designed and implemented automated Azure DevOps pipelines for the Keycloak-based SSO solution, orchestrating build, promotion, and deployment across AKS environments.
	\item Improved configuration consistency by implementing delivery-as-code through Ansible playbooks and roles, automating the provisioning of Keycloak realms, clients, and settings.
	\item Enhanced authentication capabilities of the in-house SSO solution by building 2 custom Keycloak extensions enabling 30+ enterprise clients to integrate legacy on-premises directories.
	\item Standardized branding and user experience across the company's product suite by customizing the Keycloak theme and authentication flow pages using FreeMarker templates.
\end{tightemize}
\sectionsep
\projets{Projet(s):}{In-House Keycloak-based Single Sign-On solution, Connex}
\sectionsep
\runsubsection{Géant du Web}\descript{| FullStack Web Developer}\hfill \location{Longueuil, QC | 2017 – 2018}
\begin{tightemize}
	\item Developed 10+ Joomla and WordPress websites using MVC architecture, integrating custom frontend and backend modules to deliver production-ready solutions with client-managed content.
\end{tightemize}
\sectionsep
\projets{Projet(s):}{Showcase \& Products Catalogs Websites}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Skills
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{0.8cm}
\section{Skills}
\raggedright
\begin{tabular}[t]{@{}p{0.48\textwidth}@{\hspace{0.04\textwidth}}p{0.48\textwidth}@{}}
% First column - 7 items & Second column - 7 items
{\runsubsectionlower{Cloud:}\skilldescript{Microsoft Azure}} & {\runsubsectionlower{Programming:}\skilldescript{PHP $\cdot$ C\# $\cdot$ Java}} \\[3pt]
{\runsubsectionlower{IaC:}\skilldescript{Terraform $\cdot$ Hashicorp Cloud Platform}} & {\runsubsectionlower{UI:}\skilldescript{Joomla $\cdot$ WordPress $\cdot$ Angular $\cdot$ React $\cdot$ Asp.Net}} \\[3pt]
{\runsubsectionlower{CI/CD:}\skilldescript{Azure DevOps $\cdot$ GitHub Actions}} & {\runsubsectionlower{Containers:}\skilldescript{Docker $\cdot$ K8S}} \\[3pt]
{\runsubsectionlower{VCS:}\skilldescript{GitHub $\cdot$ Azure Repos $\cdot$ Bitbucket}} & {\runsubsectionlower{Templating:}\skilldescript{Jinja2 $\cdot$ Nunjucks $\cdot$ FreeMarker}} \\[3pt]
{\runsubsectionlower{Scripting:}\skilldescript{Bash $\cdot$ PowerShell $\cdot$ Python}} & {\runsubsectionlower{CSS:}\skilldescript{sass $\cdot$ scss $\cdot$ less}} \\[3pt]
{\runsubsectionlower{CaC:}\skilldescript{Ansible (roles \& playbooks)}} & {\runsubsectionlower{Agile:}\skilldescript{SAFe $\cdot$ Scrum $\cdot$ Kanban}} \\[3pt]
{\runsubsectionlower{Artifacts:}\skilldescript{Artifactory $\cdot$ ACR $\cdot$ Azure Artifacts}} & {\runsubsectionlower{Collaboration:}\skilldescript{Jira $\cdot$ Confluence $\cdot$ Teams $\cdot$ Slack}}
\end{tabular}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Education
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{0.8cm}
\section{Education \& Certifications}
\vspace{0.4cm}
\raggedright
% \runsubsectionlower{GitHub Certified}\descript{| GitHub Actions}\hfill \location{Certified since 2025}\\
% \sectionsep
% \runsubsectionlower{GitHub Certified}\descript{| GitHub Fundamentals}\hfill \location{Certified since 2025}\\
% \sectionsep
\runsubsectionlower{Microsoft Certified}\descript{| AZ-104 | Azure Administrator Associate}\hfill \location{Certified since 2023}\\
\sectionsep
\runsubsectionlower{Microsoft Certified}\descript{| AZ-400 | Azure DevOps Engineer Expert}\hfill \location{Certified since 2023}\\
\sectionsep
\runsubsectionlower{UQAM}\descript{| Certificate in Computer Science and Software Development}\hfill \location{Montreal, QC | 2015 - 2017}\\
\sectionsep
\runsubsectionlower{University of Havana }\descript{| Bachelor’s Degree in Accounting and Finance}\hfill \location{Havana, Cuba | 2002 - 2007}\\
\sectionsep

\ 
\end{document}